---
title: "Week 2 Project Leaflet"
author: "Sean"
date: "October 12, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

#Introduction

This project will create a web page using R Markdown that features a map created with Leaflet.

The purpose of this assignment is to illustrate all mountains in Alberta, Canada. The data can be downloaded here: [LINK](https://www.nrcan.gc.ca/earth-sciences/geography/place-names/data/9245)

```{r message = FALSE}
library(leaflet)
library(dplyr)
mount <- read.csv(paste0("F:/Courses/Coursera/John_Hopkins_University_Data_Science", "/9_Developing_Data_Products/Week 2/Project/ab_geo.csv"))
colnames(mount)[colnames(mount) == "Geographical.Name"] <- "Name"
colnames(mount)[colnames(mount) == "Generic.Term"] <- "Category"
colnames(mount)[colnames(mount) == "Latitude"] <- "Lat"
colnames(mount)[colnames(mount) == "Longitude"] <- "Long"
mount2 <- select(mount, Name, Category, Lat, Long)
mount3 <- mount2[mount2$Category %in% c("Mountain", "Mountains"),]
mount3 <- mutate(mount3,
                 Name = as.character(mount3$Name))
```

__This is a list of all mountains in Alberta, you can browse it on the website, It will be better if Natural Resources Canada adding the elevation info.__

```{r}
Icon <- makeIcon(
        iconUrl = "https://image.flaticon.com/icons/svg/147/147331.svg",
        iconWidth = 36,
        iconHeight = 36*1.1,
        iconAnchorX = 36/2,
        iconAnchorY = 32
)
mount3 %>%
        leaflet() %>%
        addTiles() %>%
        addMarkers(lat = mount3$Lat,
                   lng = mount3$Long,
                   icon = Icon,
                   clusterOptions = markerClusterOptions())
```

#Name List of Mountains on Map
__This will be super long list.__
```{r message = FALSE}
library(knitr)
mount3 <- arrange(mount3, Name)
mountlist <- cbind(1:nrow(mount3),
                   mount3$Name)
kable(mountlist,
      col.names = c("", "Mountains"))
```

